\documentclass[a4paper,12pt]{article}
		\usepackage{ulem}
		\pagestyle{empty}
		\usepackage{amsmath, amssymb,amsfonts}
		\usepackage{enumerate}
		\parindent 0px
		\usepackage{hyperref}
		\usepackage{fullpage}
		\title{MY SECOND \LaTeX{} DOCUMENT}
		\author{PHILIP THEURI}
		\date{\today}
	\usepackage[margin=1cm]{geometry}
	\begin{document}
	
\tableofcontents	
\maketitle
	

\section{TEXT FORMATTING}
	
This will produce \textit{italicized} text.	
	
This will produce \textbf{bold} text.

This will produce \texttt{typewriter font} text.	
	
	This will produce \textsc{small caps} text.	
in order to write a website link in your form add the package hyperref\\	
please visit our website at \url{https://www.dkut.ac.ke/}.


for the website you can also use href instead of url as shown below

For further information, reach us through our website at \href{https://www.dkut.ac.ke/} {our official website}	
	
The displayed words our official website will take you to the destined link.\\[6pt]
it is also possible to change the font size of the sentences or words as shown below;


\begin{large}We must keep  on learning\end{large}

\begin{huge}We must keep  on learning\end{huge}

\begin{Large}We must keep  on learning\end{Large}- It has been made larger compared to the the second one due to the capital l


\begin{Huge}We must keep on learning\end{Huge}\\[0.01cm]

We must keep on learning.

\begin{small}We must keep on learning.\end{small}

\begin{scriptsize}We must keep on learning.\end{scriptsize}

\begin{tiny}We must keep on learning.\end{tiny}

if you want your lines to appear either on the left, right or center then you can use the following commands

\begin{center}
	
this line is centered
\end{center}

\begin{flushleft}this line is left justified\end{flushleft}

\begin{flushright}this line is right-justified\end{flushright}
\vspace{0.5cm}


\centering{
this line is right-justified\\
This line is left justified\\
this line is centered}
\vspace{0.3cm}
\large
{This line is enlarged\\
this is to increase the size of our line}s\\
\vspace{0.3cm}
\tiny
this line is reduced i size\\
this one too


\small
this has one has been reduced in size to a smaller extent

however it would be advisable to use the begin with and end with format to be able to track easily where it all went wrong
\vspace{0.1cm}

\normalsize
we used the slash normal size to return back the normal size.

\section{document formating}

\subsection{title and date}
For writing assignments, reports ,then it is advisable to include the date, author and the title of your document just as we included it at the top. \\[5pt]

\normalsize
However its important to note that they should come before the begin document
Choose your title appropriately.
For the date; you can type it normally or you can just use backslash today which changes with each and every time you format your document

\subsection{forming sections, subsections and subsection}
Example;We can have different titles and subtitles which are formed using the backslash format 
\section{Quadratic functions}
\subsection{vertex form}
\subsubsection{standard form}
\subsection{Factored form}
if you don't want the numbers to displayed then add an *  after the section or subsection\\
Example;
\tableofcontents
\maketitle
\section{functions}
\subsection{vertex form}
\subsubsection*{factored form}
we can make this to be a table of contents
\end{document}